% LaTeX Curriculum Vitae -- Modified by Brad Duthie
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{url}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{etaremune}
\usepackage{float}
\usepackage{longtable}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{A. Bradley Duthie}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://bradduthie.github.io/}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {data science, machine learning, statistical modelling, R, python, simulation},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\Huge \name}

\hrulefill

\vspace{0.03in}

Data Scientist and Research Software Engineer with 10+ years of experience architecting and deploying sophisticated statistical models and simulation platforms. Expert in R, statistical modelling, and agent-based simulation, with a proven record of leading complex analytical projects from concept to production. Strong background in translating complex system dynamics into scalable computational solutions and actionable insights.

\hrulefill

\vspace{0.16in}

\begin{minipage}{0.65\linewidth}
\section*{Professional Experience}
\begin{itemize}
	\item{\bf Lecturer in Environmental Modelling}, Nov. 2020 -- present \\
	University of Stirling
	\begin{itemize}
	    \item Led development and delivery of statistical programming curriculum for undergraduate students
	    \item Architected interactive R Shiny applications for teaching numerical modelling and data analysis
	    \item Managed multiple data-intensive research projects, supervising teams of researchers
	\end{itemize}
\end{itemize}
\begin{itemize}
	\item{\bf Leverhulme Trust Early Career Fellow}, Nov. 2017 -- Oct. 2020 \\
	University of Stirling
	\begin{itemize}
	    \item Secured and executed £88k research fellowship for complex systems modelling
	    \item Developed novel simulation platform for forecasting system evolution under different scenarios
	    \item Pioneered use of game-based data collection for socio-ecological decision analysis
	\end{itemize}
\end{itemize}
\begin{itemize}
	\item{\bf Postdoctoral Research Fellow}, Jun. 2013 -- Oct. 2017 \\
	Universities of Aberdeen and Stirling
	\begin{itemize}
	    \item Designed and built general-purpose simulation platform for strategy evaluation in multi-stakeholder environments
	    \item Implemented genetic algorithms for optimizing strategic decision-making
	    \item Conducted advanced statistical analysis on large ecological and social datasets
	\end{itemize}
\end{itemize}

\section*{Technical Skills}
\begin{itemize}
  \item {\bf Programming:} R (Advanced, Shiny, package development), C, Git, Linux, High-Performance Computing
  \item {\bf Modelling \& Analysis:} Statistical Modelling, Machine Learning (Genetic Algorithms), Agent-Based Modelling, Mathematical Modelling, Forecasting, Spatial Analysis
  \item {\bf Data Science:} Data Wrangling, Simulation Design, Statistical Inference, Experimental Design, Data Visualization
  \item {\bf Domains:} Complex Systems, Risk Analysis, Strategy Evaluation, Resource Management, Sustainability
\end{itemize}

\end{minipage}
\begin{minipage}{0.35\linewidth}
\fcolorbox{black}{grey!10}{
 {\small
  \begin{tabular}{ll}
  \\ 
 {\bf
 A. Bradley Duthie} \\{\bf
 Ph.D.} \\
 Data Scientist \\
 Research Software Engineer \\
 Statistical Modeller \\
 \\
 3A149 Cottrell Building \\
 University of Stirling \\
 Stirling \\
 FK9 4LA \\
 United Kingdom \\ \\ \\
 \setlength\tabcolsep{1.65pt}
 \begin{tabular}{ll}
 \Phone & (+44) 01786 467787 \\
 \Mobilefone & (+44) 07561 408101 \\
 \Envelope & \href{mailto:brad.duthie@gmail.com}{brad.duthie@gmail.com} \\
 \Mundus~ & \href{http://bradduthie.github.io}{http://bradduthie.github.io}\\ 
 \end{tabular}\\ \\
 \end{tabular}
 }
}
\end{minipage}

\section*{Key Projects \& Software}

\begin{itemize}
\item[] {\bf resevol: Spatially Explicit Simulation Platform} 
\begin{itemize}
    \item Engineered R package for simulating agricultural production and pest evolution under different management strategies
    \item Implemented in R and C with spatial modelling and genetic algorithm components
    \item Enables forecasting of system evolution and resistance development for risk assessment
    \item \href{http://CRAN.R-project.org/package=resevol}{CRAN: http://CRAN.R-project.org/package=resevol}
\end{itemize}
\end{itemize}

\begin{itemize}
\item[] {\bf GMSE: Generalised Management Strategy Evaluation}
\begin{itemize}
    \item Developed comprehensive simulation framework integrating ecological dynamics with human decision-making
    \item Used for testing intervention strategies in complex, multi-actor systems
    \item Applied to conservation conflict, resource management, and policy evaluation
    \item \href{http://CRAN.R-project.org/package=GMSE}{CRAN: http://CRAN.R-project.org/package=GMSE}
\end{itemize}
\end{itemize}

\begin{itemize}
\item[] {\bf UKRI Ecological Knowledge Games (£1.2M Project)}
\begin{itemize}
    \item Lead investigator for cross-disciplinary project developing game-based data collection and modelling
    \item Managing team of co-investigators and stakeholders across multiple institutions
    \item Focus on innovative approaches to understanding complex human-environment systems
\end{itemize}
\end{itemize}

\section*{Publications (Selected)}
\begin{etaremune}
\item {\bf Duthie, A. B.}, R. Mangan, C. R. McKeon, M. C. Tinsley, and L. F. Bussi\`{e}re. 2023. resevol: An R package for spatially explicit models of pesticide resistance given evolving pest genomes. {\it PLoS Computational Biology}. 19 (12):e1011691. \href{https://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1011691}{DOI: 10.1371/journal.pcbi.1011691}
\item {\bf Duthie, A. B.}, J. Minderman, O. S. Rakotonarivo, G. Ochoa, and N. Bunnefeld. 2021. Online multiplayer games as virtual laboratories for collecting data on socio-ecological decision-making. {\it Conservation Biology}. 35:1051-1053. \href{https://doi.org/10.1111/cobi.13633}{DOI: 10.1111/cobi.13633}
\item {\bf Duthie, A. B.}, J. J. Cusack, J. Minderman, I. L. Jones, E. B. Nilsen, R. A. Pozo, O. S. Rakotonarivo, B. Van Moorter, and N. Bunnefeld. 2018. GMSE: an R package for generalised management strategy evaluation. {\it Methods in Ecology and Evolution}. 9:2396-2401. \href{https://besjournals.onlinelibrary.wiley.com/doi/10.1111/2041-210X.13091}{DOI: 10.1111/2041-210X.13091}
\item {\bf Duthie, A. B.} 2020. Component response rate variation underlies the stability of highly complex finite systems. {\it Scientific Reports}. 10: 8296. \href{https://www.nature.com/articles/s41598-020-64401-w}{DOI: 10.1038/s41598-020-64401-w}
\end{etaremune}

\section*{Grants and Fellowships}
\vspace{-5mm}
\begin{longtable}{p{0.85\linewidth} | p{0.15\linewidth}}
\textbf{Primary Investigator} & \\

UKRI cross research council: ``Ecological Knowledge Games'' (2024) &   1,198,180 GBP \\
Leverhulme Trust Early Career Fellowship (2017) & 88,650 GBP \\
& \\
\textbf{Co-investigator} & \\
European Commission (Horizon Europe). ``Restoring Ecosystems to Stop the Threat of & 332,245 GBP \\
$\hspace{4mm}$(Re-) Emerging Infectious Diseases (RestoreID)'' (2023) &  \\
Joint Newton funded international partnership (BBSRC/FAPESP). & 620,956 GBP \\
$\hspace{4mm}$``Enhancing Diversity to Overcome Resistance Evolution'' (2019) & \\
\end{longtable}

\section*{Education}
\begin{itemize}
  \item {\bf Ph.D. Ecology and Evolutionary Biology}, 2013 \\
	Graduate Minor: Statistics \\
	Iowa State University
  \item {\bf B.S. Biology} (Magna cum laude), 2007 \\
	Specialisation: Ecology, Evolution, Environment \\
	Southern Illinois University Edwardsville
  \item {\bf B.S. Philosophy} (Magna cum laude), 2007 \\
	Minor: Chemistry \\
	Southern Illinois University Edwardsville
\end{itemize}

\section*{Leadership \& Service}
\begin{itemize}
\item {\bf Associate Editor}: Journal of Animal Ecology (2021-present; 27 manuscripts handled)
\item {\bf Manuscript Reviewer}: 50+ manuscripts for journals including {\it American Naturalist}, {\it Evolution}, {\it Proceedings of the Royal Society B}, {\it Journal of Applied Ecology}, {\it PLoS Computational Biology}
\item {\bf Grant Reviewer}: National Science Foundation (USA), L'Agence nationale de la recherche (ANR)
\item {\bf Doctoral Examiner}: Internal (2), External (1), Independent Chair (2)
\end{itemize}

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
